Dependently Typed Multi-stage Calculus

### 2019-11-20 slides/main.tex
Making vadd-gen page.

% Show grid for debug
% \setbeamertemplate{background}[grid][step=1cm]

@@

\begin{frame}[fragile]{What is Multi-stage Programming}
    A programming paradigm enables
    \begin{itemize}
        \item Generation of code at runtime
        \item Evaluation of code at runtime
    \end{itemize}
    Applications
    \begin{itemize}
        \item Speeding up programs using runtime information
    \end{itemize}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{Styles of Multi-stage Programming}
    \begin{itemize}
        \item Strings
            \begin{itemize}
                    \item Ruby, Perl, etc.
            \end{itemize}
        \item ASTs
            \begin{itemize}
                    \item Lisp
            \end{itemize}
        \item ASTs and code types
            \begin{itemize}
                    \item MetaOCaml
            \end{itemize}
    \end{itemize}
    \note{
        There are three kinds of multi-stage Programming.
    }
\end{frame}

\begin{frame}[fragile]{Example of Multi-stage Programming in MetaOCaml}
    \begin{center}
        \begin{verbatim}
     # let a = .< 1 + 2 >.;;
     val a : int code = .< 1 + 2 >.
     # Runcode.run a;;
     - : int = 3

     # let b = .<.~a + .~a>.;;
     val b : int code = .<(1 + 2) + (1 + 2)>. 
     # Runcode.run b;;
     - : int = 6
        \end{verbatim}
    \end{center}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{Application of Multi-stage Programming: vadd-gen}
    Generate efficient vector addition functions for given length vectors.
    \renewcommand{\V}{\text{Vec}}
    \begin{tabbing}
        \( \text{vadd-gen} : \I \to \TW_\alpha (\V \to \V \to \V) \) \\
        (* \( \TW_\alpha \) is corresponding to code in MetaOCaml.*) \\[2mm]
        \( \textbf{let}\ \text{vadd3} = \textbf{run}\ (\text{vadd-gen}\ 3);; \) \\
        \( \text{val}\ \text{vadd3} : \V \to \V \to \V \) \\[2mm]
        \( \text{vadd3}\ [1;2;3]\ [4;5;6];; \) \\
        \( - : \V = [5;7;9] \)
    \end{tabbing}
    \note{
    }
\end{frame}

>>>>

% Show grid for debug
\setbeamertemplate{background}[grid][step=1cm]

@@

\begin{frame}[fragile]{What is Multi-stage Programming}
    A programming paradigm enables that
    \begin{itemize}
        \item Generation of code at runtime
        \item Evaluation of code at runtime
    \end{itemize}
    Applications
    \begin{itemize}
        \item Speeding up programs using runtime information
    \end{itemize}
    \note{
    }
\end{frame}

% \begin{frame}[fragile]{Styles of Multi-stage Programming}
%     \begin{itemize}
%         \item Strings
%             \begin{itemize}
%                     \item Ruby, Perl, etc.
%             \end{itemize}
%         \item ASTs
%             \begin{itemize}
%                     \item Lisp
%             \end{itemize}
%         \item ASTs and code types
%             \begin{itemize}
%                     \item MetaOCaml
%             \end{itemize}
%     \end{itemize}
%     \note{
%         There are three kinds of multi-stage Programming.
%     }
% \end{frame}

\begin{frame}[fragile]{Example of Multi-stage Programming in MetaOCaml}
    \begin{center}
        \begin{verbatim}
     # let a = .< (1 + 2) >.;;
     val a : int code = .< (1 + 2) >.
     # run a;;
     - : int = 3

     # let b = .<(.~a) + (.~a)>.;;
     val b : int code = .< ((1 + 2) + (1 + 2)) >. 
     # run b;;
     - : int = 6
        \end{verbatim}
    \end{center}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{Application of Multi-stage Programming: vadd-gen}
    Generate efficient vector addition functions for given length vectors.
    \begin{verbatim}
 val vadd-gen : Int -> (Vec -> Vec -> Vec) code
 let vadd3 = vadd-gen 3;;
 val vadd : (Vec -> Vec -> Vec) code
 (run vadd3) [1;2;3] [4;5;6];;
  - : Vec = [5;7;9]
    \end{verbatim}
    \note{
    }
\end{frame}
